\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-10 design.tex
electives

  Elective courses can be courses within a user's major. Here, Skedge offers search, filter, and sorting features that substantially aid users in browsing courses that they might want to take.

@@

    \item ``New'' courses
    \item ``Autofit'' search\footnote{This feature is under development and is not currently live.}
    \item search by instructor
    \item Random
    \item Sorts (class size sort)

>>>>

  Elective courses can either be courses that are required for a major or minor, but are chosen by the student, or they can be courses of particular interest to students who have the flexibility to take them. For this use-case, Skedge offers search, filter, and sorting features that substantially aid users in browsing through courses and discovering ones they might want to take. Note that none of the following are supported by CDCS.

@@

    \item The Skedge DSQL includes the ``new'' keyword, which qualifies an accompanying search by only displaying the courses that were not offered the previous year for that term. For instance, searching ``new csc'' today (Fall 2016) would show Fall Computer Science courses that have been added to the catalog or changed since Fall 2015.
    \item The Skedge DSQL could include an ``autofit'' keyword, which would take into account the user's current schedule, and only show sections that would not conflict with any already scheduled times.\footnote{This feature is under development and is not currently live.}
    \item The Skedge DSQL includes the ``random'' keyword, which displays a single random course matching the accompanying query. For instance, ``random csc'' would show a random course in Computer Science for the current term. Used in conjunction with ``autofit'', it can a powerful way to find interesting new classes that are available for users to try.
    \item The Skedge DSQL includes sorting by class size---useful for students trying to find smaller, discussion based classes---or by class starting time---for students with preferences of morning or afternoon/evening classes.
    \item Because instructor names appearing in courses automatically link to searches for more courses taught by that instructor, it is easier and more natural to browse by instructor. [NEED STAT HERE]
